### 2020-02-13 README.Rmd
A first pass at local registry / local storage

```{r}
co2_url <- "http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2"
remote_register(co2_url)
```

@@

```{r}
remote_lookup("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

>>>>

```{r}
co2_url <- "http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2"
register(co2_url, "remote")
```

@@

```{r}
lookup("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37", "remote")
```
